\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-10 Thesis.tex
4.1-2 done

For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added. The exact details of this process will be explained in more detail in subsection \ref{sec:RelationalPresentations}. To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo. The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}. \ednote{check subsections}\\

@@

\begin{wrapfigure}{l}{0.3\textwidth}
\vspace{-12pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.28\textwidth]{assets/final/inclusionGraphCS}
    } 
\vspace{-16pt}
  \caption{Inclusion Graph for GenCS}
  \label{fig:inclusionGraphGenCS}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

@@

This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic. In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred. Going back to our example of Annie, an example of a subsection would be the information concerning angles. In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own. These occur on different levels as explained in the next section \autoref{sec:levels}.\\

\ednote{how to add a slide!}
by parsing the XHTML the created from the OMDocs which is then parsed and added to a presentation file. Each xhtml file represents its own slide and is hence put into its own div as shown in section \ref{sec:Impressjs}. \ednote{add picture of this}\\

With the information about the order and the dependencies of information within the paper, \sys automatically creates a presentation. It does this incrementally. As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides. After adding each slide it checks whether there is \textit{course-ancient} information, i.e. whether there are dependencies, for that slide. If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}). This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value. \ednote{code snippet}\\

@@

The system \sys parses the relational data and thus retrieves the dependencies of the topics. We already know that the level a piece of information is associated with infers that it is \textit{course-old} information. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/depGraphPythagorean}
    } 
\vspace{-5pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagorean}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

Combining this information with the order in which these pieces of information occur, i.e. with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem. We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.

@@

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.47\textwidth]{assets/final/VisualDependency}
    } 
\vspace{-5pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

If they, while browsing through these different levels, realize that they need to refresh their memory or learn more about any of the dependent information they can enter that level. The presentation will then continue on that level and give all the slides from that topic in the correct order. Once the user has gone through this short excursion, he or she can return to the initial slide and resume the normal narrative path. These modular excursions are included in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\

\ednote{meaning of moving right and down.}
\ednote {path of going through the slides - identify didactic things!!}
\ednote{show possible paths thru presentation}
\ednote{structuring of the presentation - link with primitives and spatial narrative}
\ednote{add example in slides and explain the different levels again}
\ednote {explain ids of slides}
\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}

>>>>

For including the XHTML or the PNGs we use self-created boilerplate code, in which only some coordinates and the XHTML or the PNGs for the slide are added (see \autoref{sec:Impressjs}). The details of this process will be explained in subsection \ref{sec:narrativePaths}, \ref{sec:orderedInfoGraphs}, and \ref{sec:levels}. To complement the HTML, a CSS stylesheet is added which adds the Jacobs logo. The design of the template is based on a presentation by Sebastian Wolf's \cite{Wolf:npentrel15}.\\

@@

\begin{wrapfigure}{l}{\textwidth}
\vspace{-80pt}
\end{wrapfigure}

\begin{wrapfigure}{l}{0.3\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.28\textwidth]{assets/final/inclusionGraphCS}
    } 
\vspace{-16pt}
  \caption{Inclusion Graph for GenCS}
  \label{fig:inclusionGraphGenCS}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

@@

This temporal information is also used to create narrative paths for subsections of the whole presentation that only explain one topic. In that these narrative paths are similar to the guided tours mentioned in \autoref{sec:relatedworks} in that they aim to explain one topic but they are different in that they just reuse slides that have already occurred. Going back to our example of Annie, an example of a subsection would be the information concerning angles. In essence, the \textit{intended narrative path} contains multiple \textit{narrative paths} of its own. These occur on different levels as explained in \autoref{sec:levels}.\\

@@

The system \sys parses the relational data and thus retrieves the dependencies of the topics. We already know that the level a piece of information is associated with infers that it is \textit{course-old} information \ednote{change order}. Dependencies give us the \textit{course-ancient} information, as dependencies intuitively link to information that happened more time ago.\\

@@

With the information about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the pythagorean theorem. \sys creates this presentation incrementally. As outlined in \autoref{sec:narrativePaths} and visible in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides. After adding each slide it checks whether there is \textit{course-ancient} information, i.e. whether there are dependencies, for that slide. If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}). This is achieved by keeping the \texttt{data-x} value but increasing the \texttt{data-y} value (see \autoref{fig:dependencySnippet}).\\

\begin{wrapfigure}{r}{\textwidth}
\vspace{-26pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
<div class="step slide" data-x="8750" data-y="0"> Slide </div>
<div class="step slide" data-x="8750" data-y="800"> Dependency 1 </div>
<div class="step slide" data-x="8750" data-y="1600"> Dependency 2 </div>
\end{minted}
\vspace{-5pt}
  \caption{Code Snippet for a Dependency}
  \label{fig:dependencySnippet}
  \vspace{12pt}
\end{wrapfigure}

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
    } 
\vspace{-5pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter that level. The presentation will then continue on that level and give all the slides from that topic in the correct order. Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path. These modular excursions are included in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an excursion a 90\degree rotation around the x-axis occurs and the user can now follow that story line.\\

\begin{wrapfigure}{r}{\textwidth}
\vspace{-26pt}
\begin{minted}[linenos=true, bgcolor=bg]{C}
<div class="step slide" data-x="8750" data-y="0" data-z="0" data-rotate-y="0"> Slide </div>
<div class="step slide" data-x="8750" data-y="800" data-z="0" data-rotate-y="0"> Dependency 1 </div>
<div class="step slide" data-x="8750" data-y="1600" data-z="0" data-rotate-y="0"> Dependency 2 </div>
\end{minted}
\vspace{-5pt}
  \caption{Code Snippet for a Dependency}
  \label{fig:dependencySnippet}
  \vspace{12pt}
\end{wrapfigure}

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/fullPresentation}
    } 
\vspace{-5pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

\ednote {change image}

%Combining this information with the order in which these pieces of information occur, i.e. with narrative paths and levels, we now have an ordered information graph out of which we can build a presentation that Annie can interact with to learn about the pythagorean theorem. We will look at this graph in the presentation in \autoref{sec:RelationalPresentations}.

@@

\ednote{meaning of moving right and down, rotation.}
\ednote {path of going through the slides - identify didactic things!!}
\ednote{show possible paths thru presentation}
\ednote{structuring of the presentation - link with primitives and spatial narrative}
\ednote{add example in slides and explain the different levels again}
\ednote {explain ids of slides}
\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
